Working title: Mirkovi\'c--Vybornov fusion in Beilinson--Drinfeld Grassmannian

### 2020-11-28 main.tex
mess of little meeting notes

\begin{proof}
We will prove this similarly to how the usual Mirkovi\'c--Vybornov isomorphism is proven.
\begin{enumerate}[label = Step \arabic*:]
    \item Define a map $\TT_{\mu_1, \mu_2} \cap \cN \rightarrow G_1[t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.

>>>>

\begin{proof}
We will prove this similarly to how the usual Mirkovi\'c--Vybornov isomorphism is proven.
\begin{enumerate}[label = Step \arabic*:]
    \item Define a map $\TT_{\mu_1, \mu_2} \cap \cN \rightarrow G_1[t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
    % 
    $$
    A \mapsto t^{\mu_1} (t-s)^{\mu_2} + a(t, t-s) \mapsto (L_1 \subset L_2) : (t-s)\big|_{L_2/L_1} = A\big|_{E_s}  , t\big|_{L_1/L_0} = A\big|_{E_0}
    $$
    % 
    Question: 1. is the middle matrix similar to a block matrix? 2. is the composition of these maps some intermediate level of MVy's $\psi$'s

    BD Gr as lattices? $(L_1,L_2)\in\Gr\times\Gr$ corresponds to $L$ such that $L\otimes\CC\xt\cong L_1\otimes\CC\xt$ and $L\otimes\CC\xt[t-s]\cong L_2\otimes\CC\xt[t-s]$ where $\otimes = \otimes_{\CC[t]}$ or $\otimes_{\CC[t-s]}$ respectively even though Roger believes $\CC[t] = \CC[t-s]$.
